The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-05-05 paper.tex
rework the introduction

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H}.  Following the epoch of
recombination the universe continued to expand and cool.  Small inhomogeneities observed in the CMB
grew larger and galaxies formed. The first stars formed and flooded the universe with light during
the cosmic dawn, bringing the dark ages to an end. Eventually the cumulative influence of these
galaxies completed a phase change in the inter-galactic medium (IGM), and the universe returned to
an ionized state following the conclusion of the epoch of reionization (EoR). Low frequency radio
telescopes are poised to provide the first direct detection of the IGM from the cosmic dawn and the
EoR using the redshifted hyperfine structure line of neutral hydrogen.

These low-frequency 21-cm cosmology experiments are limited by the dynamic range they can achieve
against the low-redshift sources of emission. Depending on the redshift, length scale, and model the
expected amplitude of the cosmological signal is 10 to 100 mK. On the other hand the galactic
synchrotron emission is 1000 to 10000 K. \todo{citation} Therefore experiments conservatively need
to achieve at least 4 orders of dynamic range. In theory this kind of dynamic range can be obtained
by exploiting the fact that the foreground emission is predominantly synchrotron emission that has a
smooth power law spectrum. On the other hand the frequency structure of the cosmological signal is
expected to be un-smooth because different frequencies trace different redshifts. This is the basic
assumption made by all published upper limits on the cosmological 21 cm power spectrum.  In practice
the interferometer itself imparts frequency structure into the measurements and therefore an
experiment's ability to separate the foreground signal from the cosmological signal can be limited
by the instrumental spectral smoothness.

@@

Galactic structure.

Planets?

>>>>

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
interstellar medium (ISM). Careful measurement and removal of contaminating foreground emission is
therefore an important component for CMB analysis \citep{2016A&A...594A..25P}. On large angular
scales galactic synchrotron, free-free, thermal dust, and anomolous microwave emission contribute.
On smaller angular scales point sources such as distant galaxies and quasars contribute
\citep{2016arXiv160603606D}.

Propagation effects from the IGM and intervening galaxy clusters can distort the thermal spectrum of
the CMB and impart information about the intervening material in those distortions. For instance the
measured optical depth to Thomson scattering implies a mean redshift of the Epoch of Reionization
(EoR) of ??? \todo{put number and citation}. The thermal Sunyaev--Zel'dovich effect does something
\todo{thing and citation}. The kinetic Synyaev--Zel'dovich effect does another thing \todo{thing and
citation}.

At redshifts $20 \gtrsim z \gtrsim 7$ neutral hydrogen is observable as a 10 to 100 mK perturbation
of the CMB spectrum due to the 21 cm hyperfine structure line of neutral hydrogen
\citep{2006PhR...433..181F, 2012RPPh...75h6901P}.  The spatial power spectrum of this perturbation
is expected to be dominated by inhomogeneous heating of the IGM at $z\sim 20$
\citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim 7$
\todo{citation}.

\todo{discuss more interesting science to be done}

There are numerous ongoing efforts to detect the cosmologically redshifted 21 cm transition
including from PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.

\todo{discuss global experiments too}

These low-frequency 21 cm cosmology experiments are limited by the dynamic range they can achieve
against low-redshift sources of emission. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
\end{equation}
Therefore experiments conservatively need to achieve at least 4 orders of dynamic range.  In theory
this kind of dynamic range can be obtained by exploiting the fact that the foreground emission is
predominantly synchrotron emission that has a smooth power law spectrum \todo{citation}.  In
practice the interferometer itself imparts frequency structure into the measurements and therefore
an experiment's ability to separate the foreground signal from the cosmological signal can be
limited by the instrumental spectral smoothness \todo{citation}.

@@
